Insights Into Computational Reproducibility in Plant Pathology and a Way Forward

### 2021-06-14 analysis/paper/paper.Rmd
Delete Emerson's comment, as I agree and it's implemented
Use "_" not "*" for italics

<!--# I am leaning towards a style that shows the methods at the end in a separate section? -->

@@

There are different ways to make research more open and reproducible, which can be thought of as levels of reproducibility.
The first level is including tables of raw data or code with the paper as a supplemental file.
This is suitable for studies that may have a small data set or simple analysis or for demonstrations purposes as Madden et al. [-@Madden2015] demonstrate in their discussion regarding the use of $P$ values in statistical analyses where they supply an *e-**X**tra*\* with reproducible examples for readers to refer to.
This allows the reader to quickly view the extra materials and a DOI is assigned as a part of the article itself.

At the second level, Lehner et al. [-@Lehner2017] used GitHub to host a code repository of their research compendium website with data and a reproducible report that explains in detail all steps of the analysis and the R code for conducting a meta-analysis for assessing heterogeneity in the relationship between white mold incidence and soybean yield and between incidence and soybean tied ([https://emdelponte.github.io/paper-white-mold-meta-analysis/](https://emdelponte.github.io/paper-white-mold-meta-analysis/)). The website clearly demonstrates the analysis for readers and uses R so that anyone can easily replicate the work. Likewise, Duku et al. [-@Duku2016] provide scripts for models, data and code for graphs, via a website hosted by GitHub, [http://adamhsparks.github.io/MICCORDEA/](http://adamhsparks.github.io/MICCORDEA/), that can be used to replicate their study modelling the effects of climate change on rice bacterial blight and rice leaf blast in Tanzania.

The third level is the use of proper data repositories such as FigShare, Zenodo or OSF.io among others, allow for the deposition and updating of code, figures, data preprints or any other materials that support the article itself while providing a DOI and citation for a standalone citation.
Sparks et al. [-@Sparks2011; -@Sparks2014] used FigShare to provide models, data and code, [@Sparks2016] necessary to replicate model development and the subsequent study on the effects of climate change on potato late blight.

The fourth level includes packaging the analysis as a software package, _e.g._, R, Julia or Python package at a minimum, with the use of continuous integration and possibly a software container like Docker as Khaliq et al. [@Khaliq2020] have done. Their research compendium provides a Docker instance, DOI and full R package that enable readers to fully replicate their analysis of *Ascochyta rabiei* conidia dispersal in chickpea using the data collected and stepping through other points where weather data were investigated and various models were fit before deciding on the best fit and recreate any figures as published in the article [@Khaliq2020a]. When this level is employed, tools such as Binder, [https://mybinder.org](https://mybinder.org), can be used that allow readers and reviewers to launch an interactive session in their web browser and interact with the data and rerun the analysis in an RStudio instance or Jupyter notebooks as Mioroni et al. used [-@Miorini2018, [-@Miorini2019]]. Kamvar et al. [-@Kamvar2015] took a slightly different approach by including all files necessary for the analysis and most output files in a repository [@Kamvar2014] that also included an installable R package that was used for the original analysis.
While there are many other methods, these two approaches illustrate some of the best-practices where the data and other files were deposited in repositories with DOIs and reproducibility issues were addressed by using R packages to handle dependencies and other versioning issues making the work more portable.

>>>>

@@

There are different ways to make research more open and reproducible, which can be thought of as levels of reproducibility.
The first level is including tables of raw data or code with the paper as a supplemental file.
This is suitable for studies that may have a small data set or simple analysis or for demonstrations purposes as Madden _et al._ [-@Madden2015] demonstrate in their discussion regarding the use of $P$ values in statistical analyses where they supply an _e-**X**tra_\* with reproducible examples for readers to refer to.
This allows the reader to quickly view the extra materials and a DOI is assigned as a part of the article itself.

At the second level, Lehner _et al._ [-@Lehner2017] used GitHub to host a code repository of their research compendium website with data and a reproducible report that explains in detail all steps of the analysis and the R code for conducting a meta-analysis for assessing heterogeneity in the relationship between white mold incidence and soybean yield and between incidence and soybean tied ([https://emdelponte.github.io/paper-white-mold-meta-analysis/](https://emdelponte.github.io/paper-white-mold-meta-analysis/)). The website clearly demonstrates the analysis for readers and uses R so that anyone can easily replicate the work. Likewise, Duku _et al._ [-@Duku2016] provide scripts for models, data and code for graphs, via a website hosted by GitHub, [http://adamhsparks.github.io/MICCORDEA/](http://adamhsparks.github.io/MICCORDEA/), that can be used to replicate their study modelling the effects of climate change on rice bacterial blight and rice leaf blast in Tanzania.

The third level is the use of proper data repositories such as FigShare, Zenodo or OSF.io among others, allow for the deposition and updating of code, figures, data preprints or any other materials that support the article itself while providing a DOI and citation for a standalone citation.
Sparks _et al._ [-@Sparks2011; -@Sparks2014] used FigShare to provide models, data and code, [@Sparks2016] necessary to replicate model development and the subsequent study on the effects of climate change on potato late blight.

The fourth level includes packaging the analysis as a software package, _e.g._, R, Julia or Python package at a minimum, with the use of continuous integration and possibly a software container like Docker as Khaliq _et al._ [@Khaliq2020] have done. Their research compendium provides a Docker instance, DOI and full R package that enable readers to fully replicate their analysis of _Ascochyta rabiei_ conidia dispersal in chickpea using the data collected and stepping through other points where weather data were investigated and various models were fit before deciding on the best fit and recreate any figures as published in the article [@Khaliq2020a]. When this level is employed, tools such as Binder, [https://mybinder.org](https://mybinder.org), can be used that allow readers and reviewers to launch an interactive session in their web browser and interact with the data and rerun the analysis in an RStudio instance or Jupyter notebooks as Mioroni _et al._ used [-@Miorini2018, [-@Miorini2019]]. Kamvar _et al._ [-@Kamvar2015] took a slightly different approach by including all files necessary for the analysis and most output files in a repository [@Kamvar2014] that also included an installable R package that was used for the original analysis.
While there are many other methods, these two approaches illustrate some of the best-practices where the data and other files were deposited in repositories with DOIs and reproducibility issues were addressed by using R packages to handle dependencies and other versioning issues making the work more portable.
